Results

### 2024-04-22 Analysis/04_Summarise_results.Rmd
piped data input + added time per metric plot

```{r, echo = FALSE}
library(knitr)
## Loading the results
load("../Data/Processed/sim_equalizing_2d.rda")
equalizing_2d <- bkp
load("../Data/Processed/sim_facilitation_2d.rda")
facilitation_2d <- bkp
load("../Data/Processed/sim_filtering_2d.rda")
filtering_2d <- bkp
load("../Data/Processed/sim_competition_2d.rda")
competition_2d <- bkp

## Loading the results
load("../Data/Processed/sim_equalizing_3d.rda")
equalizing_3d <- bkp
load("../Data/Processed/sim_facilitation_3d.rda")
facilitation_3d <- bkp
load("../Data/Processed/sim_filtering_3d.rda")
filtering_3d <- bkp
load("../Data/Processed/sim_competition_3d.rda")
competition_3d <- bkp

## Loading empirical results
load("../Data/Processed/empirical_data-hist-present-native.rda")
empirical_hist <- bkp
load("../Data/Processed/empirical_data-prehist-present-native.rda")
empirical_prehist <- bkp

hist_table <- empirical_hist$results_table
colnames(hist_table) <- gsub("_rm1", "_rm2", colnames(hist_table))
combined_empirical <- list()
combined_empirical$results_table <- cbind(empirical_prehist$results_table, hist_table)

## Loading the functions
source("../Functions/extract.table.R")
source("../Functions/plot.metric.results.R")
source("../Functions/paired.tests.R")
source("../Functions/split.metric.R")
source("../Functions/fit.model.rm.R")
source("../Functions/fancy.table.R")
source("../Functions/fancy.plot.R")
source("../Functions/fancy.names.R")
```

@@

```{r, echo = FALSE}
## Creating the list of results
all_results_2d <- list(equalizing   = equalizing_2d,
                       facilitation = facilitation_2d,
                       filtering    = filtering_2d,
                       competition  = competition_2d)
all_results_3d <- list(equalizing   = equalizing_3d,
                       facilitation = facilitation_3d,
                       filtering    = filtering_3d,
                       competition  = competition_3d)
empirical_results <- list(empirical = combined_empirical)

## Sort the results per name
sort.metrics <- function(one_results, order) {

@@

>>>>

```{r, echo = FALSE}
library(knitr)
## Loading the functions
source("../Functions/extract.table.R")
source("../Functions/plot.metric.results.R")
source("../Functions/paired.tests.R")
source("../Functions/split.metric.R")
source("../Functions/fit.model.rm.R")
source("../Functions/fancy.table.R")
source("../Functions/fancy.plot.R")
source("../Functions/fancy.names.R")
```

```{r, echo = FALSE}
## Loading all results per dimensions

## Simulated results:
read.results <- function(nd, stressors = c("equalizing", "facilitation", "filtering", "competition")) {
  list_load <- list()
  for(one_stressor in stressors) {
    load(paste0("../Data/Processed/sim_", one_stressor, "_", nd, ".rda"))
    list_load[[length(list_load)+1]] <- bkp
    names(list_load)[length(list_load)] <- one_stressor
  }
  return(list_load)
}

## 2d
all_results_2d <- read.results("2d")

## 3d
all_results_3d <- read.results("3d")
## placeholders
all_results_4d <- read.results("3d")
all_results_5d <- read.results("3d")
all_results_8d <- read.results("3d")

## 4d
# all_results_4d <- read.results("4d")

# 5d
# all_results_5d <- read.results("5d")

## 8d
# all_results_8d <- read.results("8d")

## Empirical

## Loading empirical results
load("../Data/Processed/empirical_data-hist-extant.rda")
#empirical_data-hist-extant
empirical_hist_extant <- bkp

load("../Data/Processed/empirical_data-prehist-hist-prehist-extant.rda")
#empirical_data-prehist-hist-prehist-extant
empirical_prehist_hist_prehist_extant <- bkp

hist_table <- empirical_hist$results_table
colnames(hist_table) <- gsub("_rm1", "_rm2", colnames(hist_table))
combined_empirical <- list()
combined_empirical$results_table <- cbind(empirical_prehist$results_table, hist_table)
empirical_results <- list(empirical = combined_empirical)
```

@@

```{r, echo = FALSE}
## Sort the results per name
sort.metrics <- function(one_results, order) {

@@

## Get the computation time per metric type

```{r}
#@ combine logical, whether to combine the results per stressor (TRUE) or not (FALSE)
get.time.per.type <- function(all_results, combine = TRUE) {
  ## Get the timers per stressor
  get.time.per.stressors <- function(one_stressor_results) {
    return(do.call(rbind, lapply(one_stressor_results$output_save, function(x) return(log(as.numeric(as.difftime(x$timer, units = "secs")))))))
  }

  ## Get all the timers
  metrics_times <- lapply(all_results, get.time.per.stressors)

  ## Combine it
  if(combine) {
    metric_times <- do.call(rbind, metrics_times)
  }
}

## times per dimensions
times_2d <- apply(get.time.per.type(all_results_2d), 2, quantile, probs = c(0.025, 0.5, 0.975))
times_3d <- apply(get.time.per.type(all_results_3d), 2, quantile, probs = c(0.025, 0.5, 0.975))
times_4d <- apply(get.time.per.type(all_results_4d), 2, quantile, probs = c(0.025, 0.5, 0.975))
times_5d <- apply(get.time.per.type(all_results_5d), 2, quantile, probs = c(0.025, 0.5, 0.975))
times_8d <- apply(get.time.per.type(all_results_8d), 2, quantile, probs = c(0.025, 0.5, 0.975))

times_tree <- cbind(times_2d[,2], times_3d[,2], times_4d[,2], times_5d[,2], times_8d[,2])
times_dissimilarity <- cbind(times_2d[,3], times_3d[,3], times_4d[,3], times_5d[,3], times_8d[,3])
times_hull <- cbind(times_2d[,4], times_3d[,4], times_4d[,4], times_5d[,4], times_8d[,4])
times_hypervolume <- cbind(times_2d[,5], times_3d[,5], times_4d[,5], times_5d[,5], times_8d[,5])
times_probabilities <-  cbind(times_2d[,6], times_3d[,6], times_4d[,6], times_5d[,6], times_8d[,6])

## Plot times per dimensions
ylim <- range(c(times_tree, times_dissimilarity, times_hull, times_hypervolume, times_probabilities))
## Plot colours
metric_cols <- c("#d55e00", "#cc79a7", "#0072b2", "#f0e442", "#009e73")

## Empty plot
plot(NULL, ylim = range(pretty(ylim)), xlim = c(2, 8), ylab = "Time (log(s))", xlab = "dimensions")

## Medians
points(x = c(2,3,4,5,8)+0.00, c(times_tree[2,]), pch = 19, col = metric_cols[1])
points(x = c(2,3,4,5,8)+0.04, c(times_dissimilarity[2,]), pch = 19, col = metric_cols[2])
points(x = c(2,3,4,5,8)+0.08, c(times_hull[2,]), pch = 19, col = metric_cols[3])
points(x = c(2,3,4,5,8)+0.12, c(times_hypervolume[2,]), pch = 19, col = metric_cols[4])
points(x = c(2,3,4,5,8)+0.16, c(times_probabilities[2,]), pch = 19, col = metric_cols[5])
## Linkings
lines(x = c(2,3,4,5,8)+0.00, c(times_tree[2,]), pch = 19, col = metric_cols[1])
lines(x = c(2,3,4,5,8)+0.04, c(times_dissimilarity[2,]), pch = 19, col = metric_cols[2])
lines(x = c(2,3,4,5,8)+0.08, c(times_hull[2,]), pch = 19, col = metric_cols[3])
lines(x = c(2,3,4,5,8)+0.12, c(times_hypervolume[2,]), pch = 19, col = metric_cols[4])
lines(x = c(2,3,4,5,8)+0.16, c(times_probabilities[2,]), pch = 19, col = metric_cols[5])
## 95% CI
dimensions <- c(2,3,4,5,8)
for(one_ci in 1:5) {
  lines(y = c(times_tree[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.00, col = metric_cols[1])
}
for(one_ci in 1:5) {
  lines(y = c(times_dissimilarity[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.04, col = metric_cols[2])
}
for(one_ci in 1:5) {
  lines(y = c(times_hull[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.08, col = metric_cols[3])
}
for(one_ci in 1:5) {
  lines(y = c(times_hypervolume[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.12, col = metric_cols[4])
}
for(one_ci in 1:5) {
  lines(y = c(times_probabilities[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.16, col = metric_cols[5])
}
## legend
legend("topleft", col = metric_cols, pch = 19, legend = c("tree", "dissimilarity", "convex hull", "hypervolume", "probability density"))
```
